Assessment and optimization of respiratory syncytial virus prophylaxis regimens in Connecticut, \Sexpr{formatYear(startDate)}-\Sexpr{formatYear(endDate)}

### 2019-03-28 Paper/RSVOptimization.rnw
Updating results to 1-week rounding

\abstractsection{Results}Using preventable fraction to assess immunoprophylaxis regimens, we found that regimens adjusted for county-level variation in RSV seasons are superior to the AAP-recommended regimen. Our best alternative to the AAP guidelines was based on the county-level RSV season midpoint; in comparison to the AAP recommendation, whose preventable fraction is \Sexpr{regionStrategyCoverage("all", "aap", 0)} (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}), that alternative yielded improvement to \Sexpr{regionStrategyCoverage("all", "countyMiddle", 1)} (\Sexpr{regionStrategyCoverageCI("all", "countyMiddle", 1, level)}).

@@

The six spatially-adjusted prophylaxis regimens yield results in all counties that are as good or better than the AAP guidelines. (Figure \ref{fig:coverageByRegionRegimen}). Statewide, the AAP guidelines offer protection to \Sexpr{regionStrategyCoverage("all", "aap", 0)} cases (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}). The least favorable of our alternative regimens --- based on statewide onset --- yields the increase to \Sexpr{regionStrategyCoverage("all", "stateOnset", 1)} (\Sexpr{regionStrategyCoverageCI("all", "stateOnset", 1, level)}); other alternative regimens yield similar results. Most of the increase comes from Hartford county, where the AAP guidelines protect \Sexpr{regionStrategyCoverage("Hartford", "aap", 0)} of cases (\Sexpr{regionStrategyCoverageCI("Hartford", "aap", 0, level)}), whereas the least favorable of our alternative regimens --- based on county-level offset --- generates an increase to \Sexpr{regionStrategyCoverage("Hartford", "countyOffset", 1)} (\Sexpr{regionStrategyCoverageCI("Hartford", "countyOnset", 1, level)}), with other alternative regimens being comparable. In every county, all alternative regimens are non-inferior to the AAP guidelines and non-superior to each other.

>>>>

\abstractsection{Results}Using preventable fraction to assess immunoprophylaxis regimens, we found that regimens adjusted for county-level variation in RSV seasons are superior to the AAP-recommended regimen. In comparison to the AAP recommendation, whose preventable fraction is \Sexpr{regionStrategyCoverage("all", "aap", 0)} (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}), our best alternative yielded improvement to \Sexpr{regionStrategyCoverage("all", "countyMiddle", 1)} (\Sexpr{regionStrategyCoverageCI("all", "countyMiddle", 1, level)}).

@@

The six spatially-adjusted prophylaxis regimens yield results in all counties that are as good or better than the AAP guidelines. (Figure \ref{fig:coverageByRegionRegimen}). Statewide, the AAP guidelines offer protection to \Sexpr{regionStrategyCoverage("all", "aap", 0)} cases (\Sexpr{regionStrategyCoverageCI("all", "aap", 0, level)}). The least favorable of our alternative regimens --- based on couty-level offset --- yields the increase to \Sexpr{regionStrategyCoverage("all", "countyOffset", 1)} (\Sexpr{regionStrategyCoverageCI("all", "countyOffset", 1, level)}); other alternative regimens yield similar results. Most of the increase comes from Hartford county, where the AAP guidelines protect \Sexpr{regionStrategyCoverage("Hartford", "aap", 0)} of cases (\Sexpr{regionStrategyCoverageCI("Hartford", "aap", 0, level)}), whereas the least favorable of our alternative regimens --- based on county-level midpoint --- generates an increase to \Sexpr{regionStrategyCoverage("Hartford", "countyMiddle", 1)} (\Sexpr{regionStrategyCoverageCI("Hartford", "countyOnset", 1, level)}), with other alternative regimens being comparable. In every county, all alternative regimens are non-inferior to the AAP guidelines and non-superior to each other.
